---
title: Session 8
author: R package build
date: '2023-12-14'
slug: session-7
categories: []
tags: []
---


```{r setup, include = FALSE, warning = FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  fig.height=4, 
  fig.width=6, 
  warning=FALSE, 
  message = FALSE,
  dev = "png", 
  dev.args = list(type = "cairo-png"))

library(tidyverse)
library(kableExtra)

options(kableExtra.html.bsTable = TRUE)

theme_set(theme_minimal() + 
            theme(plot.title = element_text(hjust = 0.5)))

celeste <- "#5e81ac"

```

```{r}
xaringanExtra::embed_xaringan(
  url = "https://r4ds-sports-session8.netlify.app/"
)
```


## Lab

1) Use [this dataset](./win_probs.rds) to create an Rmarkdown document that analyzes the win probilities for each team during the course of the game. Create a plot and include it in the file (either by inserting the `ggplot` code in an R chunk or by importing the image directly.
Use bold type to explain football concepts, bullet points to explain the main takeaways of the plot. Also add a label caption to credit the data source (`espnscrapeR` package) to the plot.

2) Use [this dataset](./diff_df.rds) to recreate the Points Differential vs. Win Percent, apply it them `ggthemes::theme_fivethirtyeight()` theme and center the plot title and subtitle.