---
title: "Session 1"
author: ''
date: '2023-09-20'
slug: session1
categories: []
tags: []
---



```{r setup, include = FALSE, warning = FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  fig.height=4, 
  fig.width=6, 
  warning=FALSE, 
  message = FALSE,
  dev = "png", 
  dev.args = list(type = "cairo-png"))

library(tidyverse)
library(kableExtra)

options(kableExtra.html.bsTable = TRUE)

theme_set(theme_minimal() + 
            theme(plot.title = element_text(hjust = 0.5)))

celeste <- "#5e81ac"

```

```{css, echo=FALSE}
.twitter-tweet {
  margin-left: auto;
  margin-right: auto;
}

blockquote {
  margin-top: 3em;
  background: hsl(0deg 0% 90%);
  padding: 16px 20px;
  border-radius: 8px;
  font-style: italic;
}

blockquote p::before {
    content: '“';
  }

blockquote p::after {
    content: '”';
  }
```


```{r}
xaringanExtra::embed_xaringan(
  url = "https://r4ds-sports-sesson1.netlify.app/"
)
```


## Lab 1

Download [this R script](./lab1.R), the [Box Score Data Frame](./box.rds) and the [Playoff Data Frame](./add.rds)

The script does the following:

- Opens two rds files with data from NBA teams.

- Merges on the `Team` column.

- Calculates the mean assits, blocks, steals for the teams that went to the playoffs and the ones that did not.

- Creates an `html` table with the results.

Your job:

- Open the script file in RStudio and run it. Make sure that it works correctly. Do Playoff teams have more points on average?

- What functions does it use?

- Can you identify which tasks each function supports (import, wrangling, model, communication)?

- What objects does it create?

- How many rows does the `df` data frame have?

- Which are the columns?
