---
title: Session 6
author: R package build
date: '2023-11-22'
slug: session-6
categories: []
tags: []
---



```{r setup, include = FALSE, warning = FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  fig.height=4, 
  fig.width=6, 
  warning=FALSE, 
  message = FALSE,
  dev = "png", 
  dev.args = list(type = "cairo-png"))

library(tidyverse)
library(kableExtra)

options(kableExtra.html.bsTable = TRUE)

theme_set(theme_minimal() + 
            theme(plot.title = element_text(hjust = 0.5)))

celeste <- "#5e81ac"

```

```{r}
xaringanExtra::embed_xaringan(
  url = "https://r4ds-sports-session6.netlify.app/"
)
```


## Lab

1) Create a bar chart with the number of minutes each player of the Houston Rockets played during the regular season. Order the players by the amount of minutes played.

2) Create a scatter plot of Offensive Pace vs. Defensive Pace for the Boston Celtics, Cleveland Cavaliers, Golden State Warriors and the Houston Rockets. Add a color mapping to show the conference of each team and a size mapping to show bigger points for teams with higher offensive rating.


3) Create a time series plot.