---
title: "R for Data Science With Sports Applications"
date: "2023-09-26"
format:
  revealjs:
    theme: default
    css: ../_styles/slides.css
    title-slide: false
    slide-number: true
    width: 1600
    height: 900
execute:
  warning: false
  message: false
  cache: false
---


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```



## Recap

- From Lab 1: it is important to keep track of where files are located in your computer.

- Your hard drive is organized in _folders_ or _directories_.

- In Mac os, `~/Desktop` is your desktop. 

- If you have a directory called lab 1 in your desktop, `~/Desktop/lab1` is the location of that folder.

- Run `setwd("~/Desktop/lab1")` to make that the working directory.

- `list.files()` prints the contents of the working directory in your console.


## Recap 2

- R code is organized in functions.

- Functions take arguments and return values.

- Data is stored in objects.

- Assignment (`<-`) makes variables point to objects.

## Recap 3

```{r}
x <- c(1, 2, 3)
mean(x)
```

```{r}
str(mtcars)
```

## Data frame

- The most important kind of object in R.

```{r}
## NBA championship 2017/2018 82 regular season games
df <- readRDS('./nba.rds')
```

## Inspect df
```{r}
df
```

##

```{r}
library(dplyr)
glimpse(df)
```

## Dplyr verbs

Key functions. Take a `data.frame` as input and return a `data.frame`. 


- `filter`
- `select`
- `mutate`
- `group_by`
- `summarize`
- `arrange`

## Filter

Filter rows from the `data.frame`.

```{r}
playoff_teams <- filter(df, Playoff=='Y')
glimpse(playoff_teams)
```

Return another data frame with the rows where the second argument is `TRUE`.

## Select

Remove columns from the data frame

```{r}
df_2 <- select(df, Team, Playoff, W, L)
glimpse(df_2)
```

## Mutate

::: {.pull-left}

Return a new data frame with a new column:
```{r}
df_rebs <- mutate(df, REB=OREB+DREB)
glimpse(df_rebs)
```
:::
::: {.pull-right}
The first argument is a `data.frame`. The rest of the arguments is one or more `expressions`. You can use formulas and mathematical operators (`-`, `+`, `*`, `/`) in those expressions.

:::

## Group By

- Returns a __grouped__ data frame.
- Does nothing to the data, but subsequent functions behave differently (`summarize`).

```{r}
df_grouped <- group_by(df, Playoff)
```


## Summarize

Returns a data frame with a summary of the argument. It will have one row per group in the argument data frame.

```{r}
tbl <- summarize(df_grouped, avg_pts=mean(PTS))
```

Like mutate, you need to pass one or more expression, that will be applied to each group in the data. 
## Arrange

- Sorts the `data.frame`
- The arguments are the columns used for sorting. 
- Use a minus sign before the argument to sort in descending order (ascending is the default)

## Arrange

- Get the top 5 ranked teams
```{r}
sorted_df <- arrange(df, Rank)
head(sorted_df, 5)
```

- Multiple arguments break ties
- How would you print only the name of the teams?


## Count

- Count how many observations for each value of the variable.
- No arguments counts all the rows
- If we pass arguments, counts grouping with the variable we passed.
```{r}
count(df)
```

- How many teams per division?
```{r}
count(df, Division)
```
## Remember object types

- Different functions take different type of objects.

- `df` is a `data.frame`
- A `data.frame` is a collection of vectors
- Vectors can be of different types
```{r}
glimpse(df)
```

We can access vectors inside a data frame in multiple ways. `$` operator.

```{r}
mean(df$PTS)
```

- Dplyr verbs streamline access to vectors

## Mutate

```{r}
df_with_mean <- mutate(df, mean_pts=mean(PTS))
```

- Think about data types!


<!-- ## Combine multiple dplyr verbs -->

<!-- - Find the top team in each division -->
<!-- ```{r} -->
<!-- grouped <- group(df, Division) -->

<!-- ``` -->

