---
title: "Session 6"
date: "2023-11-22"
format:
  revealjs:
    theme: default
    css: ../_styles/slides.css
    title-slide: false
    slide-number: true
    width: 1600
    height: 900
execute:
  warning: false
  message: false
  cache: false
---


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
library(dplyr)
library(ggplot2)
library(readxl)

if (requireNamespace("forcats", quietly = TRUE)) {
  library(forcats)
} else {
  fct_infreq <- function(f) {
    counts <- sort(table(f), decreasing = TRUE)
    factor(f, levels = names(counts))
  }

  fct_reorder <- function(.f, .x, .fun = median, ..., .desc = FALSE) {
    summary_values <- tapply(.x, .f, .fun, ...)
    levels <- names(sort(summary_values, decreasing = .desc))
    factor(.f, levels = levels)
  }
}
```



## Types

R has different types of objects.

```{r}
class(mtcars)
```

```{r}
class(c(1, 2, 3))
```

```{r}
class(c("Hello", "Goodbye"))
```


## Data Frames

- Data frames are special type of object composed of multiple objects.

```{r}
glimpse(mpg)
```


## The Manufacturer column
```{r}
mpg %>% count(manufacturer)
```

## A new type

- Factors are used to represent categorical variables
```{r}
mpg_2 <- mpg %>% 
  mutate(manufacturer=as.factor(manufacturer))

glimpse(mpg_2)
```


## Class of the vector

```{r}
class(mpg_2$manufacturer)
```

## Factors
- Behind the scenes, each category of a factor is assigned to a numeric value.
- The levels 

```{r}
levels(mpg_2$manufacturer)
```

- In this case, audi is 1, chevrolet 2, etc.
- The order of the levels is this codification.
- It is separate from the order in which the data frame is arranged.


## Forcats

- This package has functions to change the order of a factor. Think carefully about what you want.

- `fct_inorder()`: by the order in which they first appear.
 
- In this case, the alphabetical order is the same as the order in which they appear in the data. This might not be true.



## fct_infreq

- `fct_infreq()`: by number of observations with each level (largest first)

```{r}

mpg_3 <- mpg %>% 
  mutate(manufacturer=fct_infreq(manufacturer))
levels(mpg_3$manufacturer)

```



## Example

- In the NBA data, `Team`, `Playoff`, `Conference` and `Division` are factors.

```{r}
nba <- readRDS('./nba.rds')
glimpse(nba)
```



## Visualization

- Create a barchart of the number of 3 Pts attempts for the season. Add color to the bars to show if each team made the playoffs. 


##

```{r}
ggplot(data=nba, mapping=aes(Team, P3A)) +
  geom_col()
```


## Example (2)

Flipping coordinates is useful to show the labels of the Teams.
```{r}
ggplot(nba, aes(Team, P3A)) +
  geom_col() + 
  coord_flip()
```

## Order the factor

- `fct_reorder` Reorders the factor by another variable.

```{r}
nba %>% 
  mutate(Team=fct_reorder(Team, P3A)) %>% 
  ggplot(aes(Team, P3A, fill=Playoff)) +
  geom_col() +
  coord_flip()
```

## Function arguments and defaults

- You can pass arguments with or without names to functions

```{r}
nba_data <- nba %>% 
  mutate(Team=fct_reorder(Team, P3A)) 

ggplot(data=nba_data, mapping=aes(x=Team, y=P3A, fill=Playoff)) +
  geom_col() +
  coord_flip()

ggplot(nba, aes(P2A,P3A)) + geom_point()
```


## Time series plots

```{r}

df <- read_excel('./mpd2018.xlsx', sheet = 'Full data')

df_uy_usa <- df %>% 
  filter(country %in% c("Uruguay", "United States"))


plt <- df_uy_usa %>% 
  filter(year>1800) %>% 
  ggplot(aes(year, cgdppc)) + 
  geom_line(aes(group=country, color=country)) +
  scale_color_discrete("") +
  labs(title="USA leaves Uruguay behind",
       subtitle="Income gap widened last century",
       x="Year",
       y="Per Capita GDP") +
  theme_minimal() +
  theme(legend.position = "bottom")
  

```

##

```{r}
plt
```

## Facets

- Facets allow us to see different subsets of our data in different panes.


## Facets {background-image="url('./imgs/left_vs_right.png')" background-size="contain" background-position="center" background-repeat="no-repeat"}

<div class="footer-note">[Mitch Henderson](https://www.mitchhenderson.org/)</div>



## Facets in ggplot

- If we add a facetting layer to our ggplot, we get one pane for each subset of our _facetting variable_.

```{r}
xw_long <- readRDS('./xw_long.rds')
glimpse(xw_long)
```


## Facets

```{r}
stats_plot <- xw_long %>% 
  filter(stat %in% c("STL","BLK","DREB")) %>% 
  ggplot(aes(x=team, y=value, fill=stat)) +
  geom_col() + 
  coord_flip() +
  facet_grid(~stat)
```



##

```{r echo=FALSE}
stats_plot
```


## Scales

