---
title: Session 5
author: R package build
date: '2023-10-18'
slug: session-5
categories: []
tags: []
---




```{r setup, include = FALSE, warning = FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  fig.height=4, 
  fig.width=6, 
  warning=FALSE, 
  message = FALSE,
  dev = "png", 
  dev.args = list(type = "cairo-png"))

library(tidyverse)
library(kableExtra)

options(kableExtra.html.bsTable = TRUE)

theme_set(theme_minimal() + 
            theme(plot.title = element_text(hjust = 0.5)))

celeste <- "#5e81ac"

```



```{r}
xaringanExtra::embed_xaringan(
  url = "https://r4ds-sports-session5.netlify.app/"
)
```


## Lab

1) Rewrite [this R script from session 1](./script.R) to use the pipe operator.

2) Possesions are calculated with this equation (Kubatko 2007):

$$POSS = P2A + P3A + 0.44 \times FTA - OREB + TOV$$

Use the [box.rds](./box.rds) to calculate the POSS factor for each team and list the 3 teams with higher possesion values in each conference. Create a version creating intermediate variables in each step and another version using the pipe opeartor ` %>% `. Compare both approaches. 

3) Create an Rmarkdown document. The document should open [add.rds](./add.rds) and [box.rds](./box.rds). Join the two files by the `team` variable and create one table per conference with the teams that made the playoffs. The final document should look like [this](./solution.docx)


